A quick user guide to the\\ \scine-\qcm\ software suite for \mol

### 2021-02-22 dmrg/doc/qcmaquis_manual.tex

\lstdefinelanguage{molcas}
{
keywordsprefix=\&,alsoletter=\&,%
keywords=[1]{GATEWAY,SEWARD,SCF,DMRGSCF,MPSSI},
morekeywords=[2]{ActiveSpaceOptimizer,DMRGSettings,EndDMRGSettings,OOptimizationSettings,EndOOptimizationSettings,NEVPT2Prep,EvRDM,HDF5,DMRG,EJOB,SPIN,AMFI,Angmom},
keywordstyle=[1]\color{green!20!red},
keywordstyle=[2]\color{green!20!blue},
sensitive=false,
morecomment=[l]{*},
morecomment=[s]{/*}{*/},
}

@@

First, one performs a DMRG-SCF calculation with the keywords \kwd{NEVPT2Prep} and (optionally) \kwd{EvRDM}, which enable the evaluation of the 4-RDMs (and, in case of multiple states, also t-3RDMs) required by NEVPT2. If \kwd{EvRDM} is specified, the RDMs are evaluated immediately, otherwise an input file is prepared for separate RDM calculations with QCMaquis (see also Table~\ref{table:nevpt2-keyword}). The latter option is particularly useful for large active spaces, where offloaded evaluation can be performed in a massively parallel manner, which will be explained in detail in Section~\ref{sec:4rdm-distributed}.

\begin{framed}
 \noindent Note: The computational cost of the RDM evaluation grows as $N^8$ with the number of active orbitals, therefore we strongly recommend to use the distributed RDM evaluation for active spaces larger than 10-11 orbitals described in Section~\ref{sec:4rdm-distributed}.
\end{framed}

>>>>

\lstdefinelanguage{molcas}
{
keywordsprefix=\&,alsoletter=\&,%
keywords=[1]{GATEWAY,SEWARD,SCF,DMRGSCF,MPSSI},
morekeywords=[2]{ActiveSpaceOptimizer,DMRGSettings,EndDMRGSettings,OOptimizationSettings,EndOOptimizationSettings,NEVPT2Prep,HDF5,DMRG,EJOB,SPIN,AMFI,Angmom},
keywordstyle=[1]\color{green!20!red},
keywordstyle=[2]\color{green!20!blue},
sensitive=false,
morecomment=[l]{*},
morecomment=[s]{/*}{*/},
}

@@

First, one performs a DMRG-SCF calculation with the keyword \kwd{NEVPT2Prep}, which enables the evaluation of the 4-RDMs (and, in case of multiple states, also t-3RDMs) required by NEVPT2. The RDMs can be evaluated separately in a massively parallel manner, which is explained in detail in Section~\ref{sec:4rdm-distributed}.

\begin{framed}
 \noindent Note: The computational cost of the RDM evaluation grows as $N^8$ with the number of active orbitals, therefore we strongly recommend to use the distributed RDM evaluation for active spaces larger than 11-12 orbitals described in Section~\ref{sec:4rdm-distributed}.
\end{framed}
